Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2018-06-10 hpmoon-asoco.tex
Justification of the migration gap.
Adding what Martens said, but stating the obvious: it's not the focus
of this paper.

We have chosen those metrics not only because they have been used extensively, especially in some of the papers presented in Section 2 \cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Wang09parallel,Martens13asynchronous}, but also because they cover different quality criteria. Mathematical formulation of these metrics can be found in \cite{Dorronsoro13superlinear}.

@@

The number of generations between migrations has been set to 5, as
this number is usually repeated in the literature
\cite{Deb03distributed,Martens13asynchronous}. \textcolor{blue}{Migration
  is performed asynchronously, as it has the advantage of being a
  non-blocking operation \cite{TalbiUnified2018}. The individual
  chosen to migrate is selected from the subpopulation using Binary
  Tournament, as proposed in previous papers
  \cite{xiong2003parallel,Xiao03specialized}. Whenever an island
  starts the migration step, the migrated individual is sent to
  another randomly selected island. This makes it possible a
  dissemination of the modified parts of the individuals among the
  whole set of islands, thus avoiding a specific synchronization step
  to compose solutions obtained by different islands, as occurs other
  works \cite{Dorronsoro13superlinear}.} 
 The whole parameter set is summarized in Table \ref{tab:parameters}. 
 \textcolor{blue}{It is important to point out that we have carried out experiments modifying only the number of islands and the size of the problem, as other researchers have done \cite{CaoZLL17,Dorronsoro13superlinear,DorronsoroPSO2018,Martens13asynchronous,Durillo08masterslave}, who did not carry out studies on other parameters apart from these. This allows us to focus on the objective of this article, which is to demonstrate that on equal terms, the use of SLA can lead to improved performance depending on the combination of the number of islands and the size of the chromosome.}

>>>>

We have chosen those metrics not only because they have been used
extensively, especially in some of the papers presented in Section 2
% Still section 2? Please create a reference and use it - JJ
\cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Wang09parallel,Martens13asynchronous},
but also because they cover different quality criteria. Mathematical
formulation of these metrics can be found in
\cite{Dorronsoro13superlinear}.

@@

The number of generations between migrations has been set to 5,
\textcolor{blue} as
reported by \cite{Deb03distributed,Martens13asynchronous}. In general
\cite{cantu1998survey}, this migration gap has contradictory effects
on the result: by increasing it, we make the system closer to a
single-node one, since populations tend to mix without restriction; by
decreasing it, we make the isolate islands more prone to being stuck
in local minima. \cite{Martens13asynchronous} mentions that several
values were tested with no influence in the result; in our particular
case, the mixing is essential for the algorithm to spread the result
to all parts of the chromosome, so while we tend to agree with
Martens on the small influence of this value on the result, we also
think that making this value much bigger in our case would havea
negative inpact. However, a precise fine-tuning of this value is left
as future work, as the main focus of this paper was to prove the
general concept, and not tune the values for a maximum performance}.

\textcolor{blue}{This migration
  is performed asynchronously, as it has the advantage of being a
  non-blocking operation \cite{TalbiUnified2018}. The individual
  chosen to migrate is selected from the subpopulation using Binary
  Tournament, as proposed in previous papers
  \cite{xiong2003parallel,Xiao03specialized}. Whenever an island
  starts the migration step, the migrated individual is sent to
  another randomly selected island. This makes it possible a
  dissemination of the modified parts of the individuals among the
  whole set of islands, thus avoiding a specific synchronization step
  to compose solutions obtained by different islands, as occurs other
  works \cite{Dorronsoro13superlinear}.} 
 The whole parameter set is summarized in Table \ref{tab:parameters}. 
 \textcolor{blue}{It is important to point out that we have carried out experiments modifying only the number of islands and the size of the problem, as other researchers have done \cite{CaoZLL17,Dorronsoro13superlinear,DorronsoroPSO2018,Martens13asynchronous,Durillo08masterslave}, who did not carry out studies on other parameters apart from these. This allows us to focus on the objective of this article, which is to demonstrate that on equal terms, the use of SLA can lead to improved performance depending on the combination of the number of islands and the size of the chromosome.}
